A dispatch-based approach to fully allocate costs in optimal power systems

### 2020-09-09 paper/flow_based.tex
follow up

Together with the emission cost $\emissioncost$, the total OPEX $\opex$ amount around 16 billion \euro. As to expect, 99.97\% are dedicated to OCGT alone. For a detailed regional distribution of payments per MWh and the resulting revenues for generator, see \cref{fig:opex_price,fig:emission_cost}. Compared to the CAPEX allocation for OCGT, the OPEX distributes in a more local manner. This results from the fact that during ``standard'' demand peaks, it is rather local OCGT generators which serve as backup generators. In the average power mix per region, see \cref{fig:power_mix}, we observe that regions with strong OCGT capacities predominately have high shares of OCGT power. The OPEX allocations for renewables play with 0.2 \euro/MWh in average an inferior role.

>>>>

Together with the emission cost $\emissioncost$, the total OPEX $\opex$ amount around 16 billion \euro. As to expect, 99.97\% are dedicated to OCGT alone, as these have by far the highest operational price. For a detailed regional distribution of payments per MWh and the resulting revenues for generator, see \cref{fig:opex_price,fig:emission_cost}. For OCGT, the spatial allocation of the OPEX clearly differs from  the CAPEX allocation. This results from the fact that during ordinary demand peaks, it is rather local OCGT generators which serve as backup generators. In the average power mix per region, see \cref{fig:power_mix}, we observe that regions with strong OCGT capacities predominately have high shares of OCGT power. The OPEX allocations for renewables play with 0.2 \euro/MWh in average an inferior role.
